Security Audit of Safeplug

### 2014-01-13 report.tex
updated report
edited report
added outline and python script

\section{Introduction}

@@

\section{Methodology}
Safeplug is not open source, which makes a security audit much more challenging.  This leads to a debate on where a user will put his/her trust.  Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.  Wireshark allows us to capture and analyze network data \cite{wireshark}.  We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.

@@

>>>>

\section{Introduction}
    -Motivation
    -Tor
    -Safeplug

@@

\section{Procedure}
Safeplug is not open source, which makes a security audit much more challenging.  This leads to a debate on where a user will put his/her trust.  Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.  Wireshark allows us to capture and analyze network data \cite{wireshark}.  We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.

@@

\subsection{User Experience}
    -Terms of Service
    -Setup to home router
    -Using the internet
    -Experience
    -Cookie experience (Fourthparty)

\subsection{Teardown}
    -Parts in the box
    -Possible attacks via USB/SD Card

\subsection{Traffic Analysis}
    -What's the udpate?
    -Phone home frequency
    -Does it do anything else?
    -How does the ad-blocking work?

\subsection{Gaining Access through SSH}
    -How we got access
    -What's the software
    -What/where are the settings
    -RPC server
        -Attacks from anyone on local network
        -Attack from a website?

\subsection{Comparison with Tor Browser Bundle}

\section{Related Work}
TODO: Annie

\subsection{Tor}
TODO: Annie

\subsection{Fingerprinting}
TODO: Annie

\subsection{Third-party and Supercookies}
TODO: Annie
